---
title: "Analysis Report"
author: "Your Name"
output:
  pdf_document: default
  html_document: default
---
```{r}
options(repos = "https://cloud.r-project.org/")

install.packages(c("readr", "dplyr", "anytime", "plyr", "dgof", "fitdistrplus", "VGAM", "DataCombine", "data.table", "EnvStats", "ggplot2", "tsallisqexp", "poweRlaw", "fitur"))

suppressMessages(suppressWarnings({
suppressPackageStartupMessages({
  library(readr)
  library(dplyr)
  library(anytime)
  library(plyr)
  library(dgof)
  library(fitdistrplus)
  library(VGAM)
  library(DataCombine)
  library(data.table)
  library(EnvStats)
  library(ggplot2)
  library(tsallisqexp)
  library(poweRlaw)
  library(fitur)
  })


setwd("C:\\Users\\DWIGHT JIRO\\OneDrive\\Pictures\\Screenshots\\Home\\Gonzales,Dwight,M")

df1 <- read_csv("BTCUSD-2012.csv", show_col_types = FALSE)
df2 <- read_csv("BTCUSD-2013.csv", show_col_types = FALSE)
df3 <- read_csv("BTCUSD-2014.csv", show_col_types = FALSE)
df4 <- read_csv("BTCUSD-2015.csv", show_col_types = FALSE)
df5 <- read_csv("BTCUSD-2016.csv", show_col_types = FALSE)
df6 <- read_csv("BTCUSD-2017.csv", show_col_types = FALSE)
df7 <- read_csv("BTCUSD-2018.csv", show_col_types = FALSE)
df8 <- read_csv("BTCUSD-2019.csv", show_col_types = FALSE)
df9 <- read_csv("BTCUSD-2020.csv", show_col_types = FALSE)
df10 <- read_csv("BTCUSD-2021.csv", show_col_types = FALSE)
df11 <- read_csv("BTCUSD-2022.csv", show_col_types = FALSE)
df12 <- read_csv("BTCUSD-2023.csv", show_col_types = FALSE)
df13 <- read_csv("BTCUSD-2024.csv", show_col_types = FALSE)

merged_df <- bind_rows(df1, df2, df3, df4, df5, df6, df7, df8, df9, df10, df11, df12, df13)
write_csv(merged_df, "merged_data.csv")
combined_data <- read_csv("merged_data.csv", show_col_types = FALSE)

}))
  
```
### Summary of DataFrame
  
```{r}

suppressMessages(suppressWarnings({
summary(combined_data)

combined_data <- DropNA(combined_data, Var = "close", message = FALSE)
combined_data$Data <- as.Date(combined_data$timestamp, format = "%Y-%m-%d")
combined_data <- na.omit(combined_data)
df <- data.table(combined_data)

a <- aggregate(df$low, by = list(df$Data), min)
names(a) <- c("Data", "low")
b <- aggregate(df$high, by = list(df$Data), max)
names(b) <- c("Data", "high")
df <- merge(x = a, y = b, by = 'Data', all = TRUE)

df['retorno']<-NaN
df['mid']<-NaN
df[1,'mid']<-(df[1,'high']-df[1,'low'])/2+df[1,'low']
for (i in 2:nrow(df)){
df[i,'mid']<-(df[i,'high']-df[i,'low'])/2+df[i,'low']
df[i,'retorno'] <-(df[i,'mid']-df[i-1,'mid'])/df[i-1,'mid']
}

}))
```
### Histogram of BTC x USD
```{r}  
suppressMessages(suppressWarnings({

df_filtered <- na.omit(df['retorno'])

df_plot<-ggplot(df_filtered, aes(x = retorno)) +
  geom_histogram(binwidth = 0.005, fill = "blue", color = "red", alpha = 0.2) +
  labs(
    title = "Histograma of return of Bitcoin x USD",
    x = "Return",
    y = "Frequency"
  ) +
  xlim(-0.3, 0.3)

df_plot

df_teste1 <- rt(length(DropNA(df['retorno'])), length(DropNA(df['retorno'])) - 1)
ks_result1 <- ks.test(DropNA(df['retorno']), df_teste1)$statistic

df_teste2 <- rnorm(length(DropNA(df['retorno'])), mean = mean(DropNA(df['retorno'])), sd = sd(DropNA(df['retorno'])))
ks_result2 <- ks.test(DropNA(df['retorno']), df_teste2)$statistic

df_teste3 <- rlaplace(length(DropNA(df['retorno'])), mean(DropNA(df['retorno'])), sd(DropNA(df['retorno'])))
ks_result3 <- ks.test(DropNA(df['retorno']), df_teste3)$statistic

df_teste4 <- rt(length(DropNA(df['retorno'])), length(DropNA(df['retorno'])) - 1)
ks_result4 <- ks.test(DropNA(df['retorno']), df_teste4)$statistic

df_teste5 <- rnorm(length(DropNA(df['retorno'])), mean = -0.3, sd = sd(DropNA(df['retorno'])))
ks_result5 <- ks.test(DropNA(df['retorno']), df_teste5)$statistic
}))
```
### D Statistics Value
```{r}  
suppressMessages(suppressWarnings({

print("D statistic for Student:") 
print(ks_result1)
print("D statistic for Normal:") 
print(ks_result2)
print("D statistic for Laplace:")
print(ks_result3)
print("D statistic for Tsallis:")
print(ks_result4)
print("Kolmogorov-Smirnov test result:")
print(ks_result5)
}))
```
### Graph of Normal Distribution
```{r}
suppressMessages(suppressWarnings({
normal_curve <- stat_function(
  fun = dnorm,
  args = list(mean = mean(df_filtered$retorno, na.rm = FALSE), sd = sd(df_filtered$retorno, na.rm = FALSE)),
  aes(color = "Normal Distribution")
)

normald_plot <- df_plot + normal_curve +
  scale_color_manual(values = c("yellow", "blue")) +
 labs(
    title = "Histogram of return of Bitcoin x USD with Normal Distribution",
    x = "Return",
    y = "Frequency"
  )
print(normald_plot)
}))
```
### Graph of Normal Distribution
```{r}
suppressMessages(suppressWarnings({
x_values <- seq(-0.3, 0.3)
laplace_pdf <- function(x, mu, b) {
  (1 / (2 * b)) * exp(-abs(x - mu) / b)
}
laplace_d<-ggplot(df_filtered, aes(x = retorno)) +
  geom_histogram(binwidth = 0.005, fill = "blue", color = "red", alpha = 0.2) +
  stat_function(fun = laplace_pdf, args = list(mu = mean(df_filtered$retorno), b = sd(df_filtered$retorno)),
                aes(color = "Laplace Distribution")) +
  scale_color_manual(values = c("Laplace Distribution" = "green")) +
  labs(
    title = "Histogram of return of Bitcoin x USD with Laplace Distribution",
    x = "Return",
    y = "Frequency"
  ) +
  xlim(-0.3, 0.3)

print(laplace_d)
}))
```
### Summary

After conducting a thorough analysis of the data and statistical tests, it is evident that the Laplace Distribution provides the best fit for modeling the return of Bitcoin against USD. This conclusion is based on the D statistic comparison across different distributions











